Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/responseToReviewers.tex

\item \emph{All the justifications arise from psychoacoustics, bioacoustics ... when the challenge is to classify ambient non natural stationary sounds. For example, the whole Gammatone wavelet justification over Morlet is biased.}

While some of the sounds are ``non-natural'', that is human-caused, that does not make differentiating between them an impossible task for a biological system evolved under exposure to other, more ``natural'' sounds. In addition, the psychoacoustic results cited have been obtained by conducting experiments where subjects listened to the same type of ``non-natural'' sounds. As such, we feel that the justifications are well-adapted to our method and tasks.

\item \emph{The classification accuracy is not suited for comparison since the dimension of the feature vectors are not the same for all the techniques.}

While the dimension of the features vectors are different, this does not necessarily have to impact the performance of the classification. For example, if we were classifiying stationary Gaussian signals, a spectral envelope feature, like the MFCCs, would prove to be just as accurate, if not better, than the richer second-order scattering transform. The important relationship to consider is whether the feature transform provides an accurate description of the relevant information content in the signal. In addition, most of our experiments deal with the feature vectors through an RBF kernel, which is equivalent to considering the features embedded in an infinite-dimensional space, so in this sense the original dimensionality of the feature vectors carries less importance. A paragraph has been added to discuss the influence of dimensionality.

@@

\item \emph{The used descriptors are only locally time shift invariant and not globally which is never pointed out.}

As formulated, the scattering transforms do indeed have only local time-shifting invariance, which has been clarified. However, the processing corresponding to ``early'' integrating achieves more invariance through complete averaging of the scattering transform along time and so does have that global time-shifting invariance.

\item \emph{The function $\phi$ is hardly considered as a low-pass since a low-pass is only used in coordination with a high-pass for quadratic mirror filters. Here $\phi$ is a scaling function.}

The function $\phi$ is very much a low-pass filter with a frequency support of approximately $1/T$ and a time bandwidth of $T$, where $T$ is of the order of hundreds of milliseconds. It does not correspond to the traditional scaling function used in quadrature mirror filters.

@@

\item \emph{The scattering network is defined with an infinite cascade of transform yet it is enough to compute two layers, why?}

For the time scales considered in this paper, the first two orders are sufficient to describe the sound events present in the signals. This has been made clearer in the text.

\item \emph{It is never specified what are the signals frequency sampling which we have to deduce to be 44100 Hz from line 9 page 3 "20kHz close to the Nyquist frequency of the audio recordings".}

It is true that the audio recordings from the DCASE 2013 and 2016 datasets are sampled at 44100 Hz. This information has been added in Section VII.A.

@@

\item \emph{Setting of $Q1$ shall be motivated.}

This has been added to the text.

\item \emph{Reproducibility:  data sets are publicly available, the author do not mention if they plan to make their model available.}

Experiments have been performed in the MATLAB environment using open source libraries an all the authors are committed to comply to the reproducible research statements. The replication code is now available in beta, and will be soon stable.

@@

\item \emph{In the last experience (Table III) GMM (MFCC) may be compared to SVM (MFCC) (in addition to SVM (logscat)). There is somewhere a high dimension effect that shall be clarified.}

We have added results for SVM on MFCCs. As mentioned in the response to the other reviewer, we believe that the high dimensionality should not have a significant effect on these results, even though we acknowledge that this effect would be interesting to study. Our justification have been added to the manuscript.

@@

\item \emph{The cross-validation analyses confirmed that the value T = 372 ms for the support of the low-pass filter is optimal when applying late integration by majority voting, but shall it adapted per classes  ?}

Although it is true that different values of $T$ could be appropriate for different classes (that is, the different sound objects present could be of different scale), we do not expect results to change significantly. This is because the sounds are of a similar nature (ambient, non-directed) and so any distinct object shouldn't be much longer or shorter in duration in one class compared to another. In addition, $T = 372\,\mathrm{ms}$ is at the longer end of the useful range of window sizes for which the scattering transform is useful, so it is unlikely that larger sizes would improve.

\item \emph{A table with the 2016 DCASE private results may be added (or replace Tab III).}

The private results have been reported in terms of the average class accuracy, but due to lack of space, we have not included the per-class results. However, we do provide a link to the website where these can be viewed.

### 2016-12-20 paper/structureScene.tex
edit results Table I
edit results supervised: "albeit consistent" => "over all but one"
edit RbQ results

\begin{table}
\begin{center}
\caption{
\label{table:dcase2013}
Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.
}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
\emph{early}, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
\emph{early}, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
\emph{late}, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
\emph{late}, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\end{center}
\end{table}

@@

Logarithmic compression provides a small, albeit consistent boost to acoustic scene classification over all folds in the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).

@@

For the scattering transform, both \emph{RbQ-c} and \emph{RbQ-w} outperform \emph{early}, thus confirming the benefits of using an relevance-based quantization (RbQ) to improve the similarity measures between the scenes. However, it is worth noticing that \emph{RbQ-a} performs comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. To take advantage of an such a representation, we need to select certain representative centroids when comparing quantized objects. Furthermore, it appears that \emph{RbQ-c} is better able to characterize the classes than \emph{RbQ-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources with only a few sources discriminating between them.

>>>>

\begin{table}
\begin{center}
\caption{
\label{table:dcase2013}
Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.
}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
\emph{early}, linear  & $54\pm19$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
\emph{early}, RBF     & $47\pm16$  & $61\pm\phantom{0}9$  & $63\pm\phantom{0}6$   \\
\emph{late}, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
\emph{late}, RBF     & $68\pm14$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\end{center}
\end{table}

@@

Logarithmic compression provides a small boost to acoustic scene classification over all but one fold of the DCASE 2013 private dataset.
Indeed, as discussed in subsection \ref{sec:logcomp}, and observed in Figure \ref{fig:compression}, the statistical assumption of normality for scattering coefficients is only approximately satisfied once mapped to a logarithmic, decibel-like scale. This transformation improves the discriminative power of the SVMs trained on scattering coefficients, regardless of the chosen temporal integration strategy (early or late) and the inner product kernel (linear or Gaussian RBF).

@@

For the scattering transform, both \emph{RbQ-c} and \emph{RbQ-w} outperform \emph{early}, thus confirming the benefits of using an relevance-based quantization (RbQ) to improve the similarity measures between the scenes. However, it is worth noticing that \emph{RbQ-a} performs worse or comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. To take advantage of an such a representation, we need to select certain representative centroids when comparing quantized objects. Furthermore, it appears that \emph{RbQ-c} is better able to characterize the classes than \emph{RbQ-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources with only a few sources discriminating between them.
